Of judges, aliens and total preorders

### 2021-02-15 presentation/1901_3230880_philip_heltweg_presentation.tex
feat: some more slides

\begin{frame}{A concrete operator}
    \note{
        \begin{itemize}
            \item math for operator
        \end{itemize}
    }
\end{frame}

\begin{frame}{Courtroom Example: A concrete operator}
    \note{
        \begin{itemize}
            \item math for example with operator
        \end{itemize}
    }
\end{frame}

\begin{frame}{Courtroom Example: Visualised}
    \note{
        \begin{itemize}
            \item figure 6
        \end{itemize}
    }
\end{frame}

\begin{frame}{Courtroom Example: Conditional beliefs 1}
    \note{
        \begin{itemize}
            \item figure 7
        \end{itemize}
    }
\end{frame}

\begin{frame}{Courtroom Example: Conditional beliefs 2}
    \note{
        \begin{itemize}
            \item figure 8
        \end{itemize}
    }
\end{frame}

\section{Final remarks}

@@

\begin{frame}{Sample frame title}
    This is a text in the first frame. This is a text in the first frame. This is a text in the first frame.
\end{frame}

\begin{frame}
\frametitle{Sample frame title}

In this slide, some important text will be
\alert{highlighted} because it's important.
Please, don't abuse it.

\begin{block}{Remark}
Sample text
\end{block}

\begin{alertblock}{Important theorem}
Sample text in red box
\end{alertblock}

\begin{examples}
Sample text in green box. The title of the block is ``Examples".
\end{examples}
\end{frame}

\section{More examples}

\begin{frame}
\frametitle{Two-column slide}

\begin{columns}

\column{0.5\textwidth}
This is a text in first column.
$$E=mc^2$$
\begin{itemize}
\item First item
\item Second item
\end{itemize}

\column{0.5\textwidth}
This text will be in the second column
and on a second tought this is a nice looking
layout in some cases.
\end{columns}
\end{frame}

>>>>

\begin{frame}{A concrete operator}
    \begin{itemize}
        \item $p: W^{\pm} \mapsto \mathds{R}$
        \item $p(x^{-}) - p(x^{+}) = a > 0$
        \item $x^{\epsilon} \preceq_{p} y^{\delta} \textrm{ iff } p(x^{\epsilon}) \leq p(y^{\delta})$
        \item Set $p$, for every $x^{\epsilon} \in W^{\pm}$, to:
    \end{itemize}

    \begin{equation*}
        (p \ast \alpha)(x^{\epsilon}) = \left\{
                        \begin{array}{ll}
                          p(x^{\epsilon}) \textrm{ if } x \in \modelsOf{\alpha}\\
                          p(x^{\epsilon}) + a \textrm{ if } x \in \modelsOf{\neg\alpha}
                        \end{array}
                      \right.
    \end{equation*}

    \note{
        \begin{itemize}
            \item math for operator
        \end{itemize}
    }
\end{frame}

\begin{frame}{Courtroom Example: A concrete operator}
    \begin{itemize}
        \item Choose initial $p$ so that $\preceq_{p} = \preceq$
        \begin{itemize}
            \item $010 \textrm{ : } (p(010^{+}), p(010^{-})) = (0, a)$.
            \item $100 \textrm{ : } (p(100^{+}), p(100^{-})) = (0, a)$.
        \end{itemize}
        \item Revise $p$ by $\alpha$ to $p \ast \alpha$
        \begin{itemize}
            \item $010 \in \modelsOf{\neg\alpha} \textrm{ : } (p(010^{-}), p(010^{-}) + a) = (a, 2a)$
            \item $100 \in \modelsOf{\alpha} \textrm{ : } (p(100^{+}), p(100^{-})) = (0, a)$
        \end{itemize}
            \end{itemize}

    \note{
        \begin{itemize}
            \item math for example with operator
        \end{itemize}
    }
\end{frame}

\begin{frame}[fragile]{Courtroom Example: Visualised}
    \begin{figure}[H]
            \centering
            \begin{tikzpicture}[scale=1]
                \begin{axis}[
                        xticklabels={},
                        yticklabels={},
                        extra y ticks={1, 2, 3, 4, 5, 6, 7, 8},
                        extra y tick labels={$111$, $001$, $101$, $011$, $110$, $000$, $100$, $010$},
                        ytick style={draw=none},
                        xtick style={draw=none},
                        axis line style={draw=none}
                ]
                \addplot[
                    scatter,
                    scatter src=explicit symbolic,
                    mark size=3,
                    scatter/classes={
                        empty={mark=*, fill=white},
                        old={mark=x, fill=white}
                    },
                    nodes near coords*={\Label},
                    visualization depends on={value \thisrow{label} \as \Label}
                ]
                table [meta=class] {
                        x y class label

                        1 8 old \empty

                        3 8 empty
                        5 8 empty

                        2 6 old

                        4 6 empty
                        6 6 empty

                        5 4 old

                        7 4 empty
                        9 4 empty

                        6 2 old

                        8 2 empty
                        10 2 empty

                        6 1 empty 
                        8 1 empty
                        };
                \end{axis}
            \end{tikzpicture}
            \caption{$\preceq_{p \ast \alpha}$ for $\alpha = p$}
            \label{fig:example-preceq-revised}
    \end{figure}

    \note{
        \begin{itemize}
            \item figure 7
        \end{itemize}
    }
\end{frame}

\begin{frame}[fragile]{Courtroom Example: Conditional beliefs 1}
    \begin{figure}[H]
            \centering
            \begin{tikzpicture}[scale=1]
                \begin{axis}[
                        xticklabels={},
                        yticklabels={},
                        extra y ticks={1, 2, 3, 4, 5, 6, 7, 8},
                        extra y tick labels={$111$, $001$, $101$, $011$, $110$, $000$, $100$, $010$},
                        ytick style={draw=none},
                        xtick style={draw=none},
                        axis line style={draw=none}
                ]
                \addplot[
                    scatter,
                    scatter src=explicit symbolic,
                    mark size=3,
                    scatter/classes={
                        empty={mark=*, fill=white},
                        old={mark=x, fill=white}
                    },
                    nodes near coords*={\Label},
                    visualization depends on={value \thisrow{label} \as \Label}
                ]
                table [meta=class] {
                        x y class label

                        1 8 old \empty

                        3 8 empty
                        5 8 empty

                        1 7 old

                        3 7 empty 
                        5 7 empty

                        2 6 old

                        4 6 empty
                        6 6 empty

                        2 5 old

                        4 5 empty 
                        6 5 empty

                        6 1 empty 
                        8 1 empty
                        };
                \end{axis}
            \end{tikzpicture}
            \caption{$\preceq_{p \ast \alpha}$ for $\alpha = r$}
            \label{fig:example-preceq-revised-alien}
    \end{figure}

    \note{
        \begin{itemize}
            \item figure 8
        \end{itemize}
    }
\end{frame}

\begin{frame}[fragile]{Courtroom Example: Conditional beliefs 2}
    \begin{figure}[H]
            \centering
            \begin{tikzpicture}[scale=1]
                \begin{axis}[
                        xticklabels={},
                        yticklabels={},
                        extra y ticks={1, 2, 3, 4, 5, 6, 7, 8},
                        extra y tick labels={$111$, $001$, $101$, $011$, $110$, $000$, $100$, $010$},
                        ytick style={draw=none},
                        xtick style={draw=none},
                        axis line style={draw=none}
                ]
                \addplot[
                    scatter,
                    scatter src=explicit symbolic,
                    mark size=3,
                    scatter/classes={
                        empty={mark=*, fill=white},
                        filled={mark=*, fill=black},
                        old={mark=x, fill=white}
                    },
                    nodes near coords*={\Label},
                    visualization depends on={value \thisrow{label} \as \Label}
                ]
                table [meta=class] {
                        x y class label

                        1 8 old \empty

                        3 8 filled
                        5 8 empty

                        1 7 old

                        3 7 filled 
                        5 7 empty

                        2 6 old

                        4 6 empty
                        6 6 filled

                        2 5 old

                        4 5 empty 
                        6 5 filled

                        5 4 filled
                        7 4 empty

                        6 1 empty 
                        8 1 filled
                        };
                \end{axis}
            \end{tikzpicture}
            \caption{$\preceq_{p \ast \alpha \ast \beta}$ for $\beta = (p \vee q) \wedge (\neg p \vee \neg q)$}
            \label{fig:example-preceq-revised-alien2}
    \end{figure}

    \note{
        \begin{itemize}
            \item figure 9
        \end{itemize}
    }
\end{frame}

\begin{frame}{}
  \centering \Huge
  Thank You
\end{frame}

@@
